References

### 2015-01-04 cv/XieXiaolei-Computing.tex
Add CV and cover letters.

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsfonts, amsmath}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[sc,osf]{mathpazo}

@@

% Place name at left
{\huge Xie Xiaolei}

@@

\section*{Education}
\begin{itemize}
\item Ph.D of Financial Mathematics, October 2014 - present
  \begin{itemize}
    \item {\it Reseach Areas:} I am mainly interested in the
      determination of the largest eigenvalues of a covariance matrix
      built from samples with heavy-tails. The purpose is dimension
      reduction, by which the behaviour of a diverse portfolio is
      replicated by one with much few components and hence analysis of
      the portfolio becomes more simplified and focused.

      I am also interested in efficient simulation of multivariate
      GARCH structures, which, among others, helps the determination of
      model parameters when fitting such a model to a large
      multi-dimensional data set.
  \end{itemize}

\item Master of Physics, Lund University, January 2011 - June 2014
  \begin{itemize}
  \item {\it Major Subject:} Econophysics. In my thesis I studied the
    average eigenvalue distribution of sample covariance matrices,
    with a focus on the impact of autocorrelations and heavy tails.

    % The returns' models are fitted to such Swedish stocks as Volvo B,
    % Ericsson B, and Nordea Bank, using both publicly available daily
    % statistics and intra-day transaction data that I have been
    % collecting using home-developed software.

    % The studies are carried out analytically wherever feasible, and
    % otherwise by approximation and simulation. The application of
    % probability theories, random matrices, and stochastic processes
    % are the most involved subjects.
  \end{itemize}

\item M.Sc.(Tech) Computer Science and Engineering, Helsinki
  University of Technology, 2005 - 2008.
  \begin{itemize}
  \item {\it Major Subject:} Mobile Computing - Services and Security
  \item {\it Average grade:} 4.17/5.
  \end{itemize}

\item B.Sc. Computer Science \& Technology, Beijing Institute of
  Technology, 2001- 2005.
  \begin{itemize}
  \item {\it Average grade:} 85.5/100.
  \item {\it Honors:} \textit{Distinguished Graduates of 2005}.
  \end{itemize}
\end{itemize}

@@

  My main responsibility is software development in C, and sometimes
  C++ and Java, in the Linux operating system.

@@

  Funded by HIIT, I wrote my thesis ``A Mutual authentication and Key
  Agreement Protocol for the UMTS Network''. The algorithm of my
  protocol proposal was based on the Diffie-Hellman Exchange, but had
  significant modifications and extensions so that the mutual
  authentication between the mobile user and the network was delegated
  to the serving instead of the home network. The protocol design
  incorporated puzzle schemes that demanded unbalanced computing
  resources on the two sides to mitigate Denial-of-Service attacks.

\item {\it May 2007 - April 2004}
  I worked as software engineer in several companies. The programming
  languages used included C, C++, Java and python.
\end{aperiod}

\section*{Private Project}
{\it Trade data collector and analyzer}
With this home-developed software I have been collecting intra-day
transaction data and analyzing them in real-time with Matlab. I make
heavy use of the Matlab economitrics toolbox with its built-in
routines for estimating ARIMA and GARCH models and then forecasting
using the obtained model. The idea is to pre-estimate a model and thus
fix its structure, such as the distribution of the residuals, the
order of the auto-regressive and the moving-average components, the
order of differencing/fractional differencing, etc., and then to 
evolve the model parameters in real-time as new data are fed into
the system.
\end{document}

>>>>

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[sc,osf]{mathpazo}

@@

% Place name at left
{\huge \name}

@@

\section*{Education}
\begin{itemize}
\item Master of Physics, Lund University, January 2011 - June 2014.
  \begin{itemize}
  \item {\it Major Subject:} Econophysics. My thesis project was
    case studying of intraday returns of Nordea, Volvo and
    Ericsson. Covariance matrices of GARCH and stochastic volatility
    returns were also studied. Matlab programming was a crucial part.
  \end{itemize}
\item M.Sc.(Tech) Computer Science and Engineering, Helsinki
  University of Technology, 2005 - 2008.
  \begin{itemize}
  \item {\it Major Subject:} Mobile Computing - Services and Security
  \item {\it Average grade:} 4.17/5.
  \end{itemize}
\item B.Sc. Computer Science \& Technology, Beijing Institute of
  Technology, 2001- 2005.
  \begin{itemize}
  \item {\it Average grade:} 85.5/100.
  \item {\it Honors:} \textit{Distinguished Graduates of 2005}.
  \end{itemize}
\end{itemize}

@@

  My responsibilities included developing audio low-level software,
  typically device drivers, in the Linux OS. This involved designing and
  implementing data structures and procedures so that the hardware
  devices were used in the optimal way, in terms of parallelism,
  power consumption, robustness, and ease of maintenance.

@@

  Funded by HIIT, I wrote my thesis ``A Mutual authentication and Key
  Agreement Protocol for the UMTS Network''. The algorithm of my
  protocol proposal was based on the Diffie-Hellman Exchange, but had
  significant modifications and extensions so that the mutual
  authentication between the mobile user and the network was delegated
  to the serving instead of the home network. The protocol design
  incorporated puzzle schemes that demanded unbalanced computing
  resources on the two sides to mitigate Denial-of-Service attacks. I
  made C programs to test the puzzle schemes.

\item {\it
    \href{http://www.goodmillsystems.com}{\tt Goodmillsystems},
    Software Designer, May 2007 - Sep 2007}

  I developed a daemon program that ran on the company's smart router
  product to collect statistical data about the router's network
  traffic. The emphasis of the program was high performance in the
  context of competing read and write accesses.

\item {\it \href{http://www.cardinal.fi/}{\tt
      Cardinal Information Systems}, Software Developer, Sep 2006 -
    April 2007}

  I implemented the FLUTE protocol for the company's DVB-H
  mobile-end middleware. The implementation was multi-threaded and was
  built on the {\it pthread} library. Good performance and robustness
  were crucial requirements on the implementation.

\item {\it
    \href{http://www.digitalchocolate.com/}{\tt Digital Chocolate},
    Game Engineer, Feb 2006 - Sep 2006}

  At this job, my responsibilities were porting and customizing mobile
  phone games for various handsets, and making game demos.

\item {\it {\tt Beijing Holystone Ltd}, Software
    Engineer, April 2004 - June 2005}

  At this job I mainly developed JSP pages and database routines for
  the company's information system.
\end{aperiod}

\section*{Personal Project}
{\it Trades data collector \& Analyzer}

I have been developing my own stock-trading robot since the summer of
2011. It is a software built on cURL, GLib, MySQL, and Matlab. I find
it a fairly interesting, challenging, and rewarding combination of
programming skills, data analysis techniques, and knowledge of
financial time series. My knowledge in econophysics guides the
development of this software.

\section*{Non-English Language Skills}
\begin{itemize}
\item Swedish: informal communications. ``Swedish B'' passed.
\item Chinese: Native speaker
\end{itemize}

\end{document}

### 2015-01-04 cv/XieXiaolei.tex
Add CV and cover letters.

\usepackage{marvosym} % Required for symbols in the colored box
\usepackage{ifsym} % Required for symbols in the colored box

@@

\par{\centering{\sffamily\Huge John Smith}\\ % Your name
{\color{headings}\fontspec[Variant = 2]{Century Schoolbook L} Curriculum {Vit\fontspec[Variant = 3]{Century Schoolbook L}\ae}\\[15pt]\par} % Curriculum vitae text in the Century Schoolbook L font

@@

\begin{minipage}[t]{0.5\textwidth} % Start the left-hand side of the page
\vspace{0pt} % Trick for alignment

@@

{\raggedleft\textsc{Current, from Jan 2009}\par}

{\raggedright\large Trader at Enoi s.p.a., Milan\\
\textit{Physical Natural Gas Trading}\\[5pt]}

\normalsize{Provided analysis of spreads, in particular time and location spreads, with emphasis on trading opportunities on the curve, also taking into account the availability of storage facilities. Became familiar with logistic implications of physical gas trading and developed knowledge of continental virtual hubs for gas exchange.}\\

@@

{\raggedleft\textsc{July 2008 -- Oct 2008}\par}

{\raggedright\large 1\textsuperscript{st} year Analyst at \textsc{Lehman Brothers}, London\\
\textit{Commodities Structured Trading}\\[5pt]}

\normalsize{Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping.}\\

@@

{\raggedleft\textsc{Summer 2007}\par}

{\raggedright\large Summer Intern at \textsc{Lehman Brothers}\\
\textit{Capital Markets}\\[5pt]}

\normalsize{Received pre-placed offer from the Exotics Trading Desk as a result of very positive review. Rated ``truly distinctive" for Analytical Skills and Teamwork.}\\

%------------------------------------------------
% WORK EXPERIENCE 4
%------------------------------------------------

{\raggedleft\textsc{Current, from Jan 2009}\par}

{\raggedright\large Trader at Enoi s.p.a., Milan\\
\textit{Physical Natural Gas Trading}\\[5pt]}

\normalsize{Provided analysis of spreads, in particular time and location spreads, with emphasis on trading opportunities on the curve, also taking into account the availability of storage facilities. Became familiar with logistic implications of physical gas trading and developed knowledge of continental virtual hubs for gas exchange.}\\

%------------------------------------------------
% WORK EXPERIENCE 5
%------------------------------------------------

{\raggedleft\textsc{July 2008 -- Oct 2008}\par}

{\raggedright\large 1\textsuperscript{st} year Analyst at \textsc{Lehman Brothers}, London\\
\textit{Commodities Structured Trading}\\[5pt]}

\normalsize{Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping.}\\

\colorbox{shade}{\textcolor{text1}{
\begin{tabular}{c|p{7cm}}
\raisebox{-4pt}{\textifsymbol{18}} & 123 Broadway, City, State 12345 \\ % Address
\raisebox{-3pt}{\Mobilefone} & +1 (1)23 4567890 \\ % Phone number
\raisebox{-1pt}{\Letter} & \href{mailto:john@smith.com}{john@smith.com} \\ % Email address
\Keyboard & \href{http://www.johnsmith.com}{http://www.johnsmith.com} \\ % Website
\end{tabular}
}
}\\[10pt]

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{tabular}{rl} % Start a table with two columns, one for dates and one for qualifications

%------------------------------------------------
% EDUCATION 1
%------------------------------------------------

2011 -- \textsc{Present} & \textbf{Doctor of Philosophy} \\ 
& \textsc{Computer Science} \\ 
& \textit{The University of California}\\
&\\

%------------------------------------------------
% EDUCATION 2
%------------------------------------------------

2010 & \textbf{Master of Science} \\ 
& \small First Class Honours \\
& \textsc{Computer Science} \\ 
& \textit{The University of California}\\
&\\

%------------------------------------------------
% EDUCATION 3
%------------------------------------------------

2009 & \textbf{Postgraduate Diploma}\\
& \small Distinction \\
& \textsc{Computer Science} \\
& \textit{The University of California}\\
&\\

%------------------------------------------------
% EDUCATION 4
%------------------------------------------------

2006 -- 2008 & \textbf{Bachelor of Business Studies}\\
& \textsc{Commerce} \\
& \textit{The University of California}

\end{tabular}\\[10pt]

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\section{Awards}

\begin{tabular}{rl}
2010	 & \textbf{Faculty of Science Masters Scholarship}\\
& \textit{The University of California}\\ \\

%------------------------------------------------

2008	 & \textbf{Top Achiever Award -- Commerce}\\
& \textit{Business Association of California}
\end{tabular}\\[10pt]

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\section{Computer Skills}

\begin{tabular}{rl}
Basic Knowledge
& \textsc{java}, Adobe Illustrator\\ 
& \\
Intermediate Knowledge
& \textsc{python}, \textsc{html}, \LaTeX,\\
& OpenOffice, Linux,\\
& Microsoft Windows \\
& Computer Hardware \& \\
& Support\\ \\
\end{tabular}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS
%----------------------------------------------------------------------------------------

\section{Communication Skills}

\begin{tabular}{rl}
\textsc{Conferences}
& Oral Presentation at the California \\
& Computer Science Conference -- 2010\\
& \\
\textsc{Posters}
& Poster at the Annual Programming \\
& Conference in Oregon -- 2009 \\
\end{tabular}\\[10pt]

>>>>

\usepackage{wasysym}
\usepackage{marvosym} % Required for symbols in the colored box
\usepackage{ifsym} % Required for symbols in the colored box

@@

\par{\centering{\sffamily\Huge Xie Xiaolei}\\ % Your name
{\color{headings}\fontspec{Century Schoolbook L} Curriculum {Vit\fontspec{Century Schoolbook L}\ae}\\[15pt]\par} % Curriculum vitae text in the Century Schoolbook L font

@@

\begin{minipage}[t]{0.5\textwidth} % Start the left-hand side of the page
%\vspace{0pt} % Trick for alignment
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education} 
\begin{itemize} 
\item \textit{Lund University, Sweden}

\begin{tabular}{l p{0.7\textwidth}}
  2011 -- \textsc{Present} & {M.Sc. Econophysics: Mathematical
  Physics in Finance} \\
  Thesis title & Returns Models and Their Covariance Matrix \\
  Description & Compared accuracy of volatility forecasts of {\bf
    GARCH} and {\bf stochastic volatility} (SV) models by case
  studying Nordea, Volvo and Ericsson {\bf intraday} returns using the
  two classes of models. Realized volatilities were computed and
  compared to the forecasts. Also studied eigenvalues' distribution of
  a covariance matrix of GARCH returns. {\bf MATLAB} programming was
  an essential part.
\end{tabular}

\item {\it Helsinki University of Technology, Finland}

\begin{tabular}{l p{0.7\textwidth}}
  2005 -- 2008 & {\bf M.Sc. Computer Science} \\
  Thesis Title & A Mutual Authentication and Key Agreement Protocol
  for the UMTS Network \\
  Description & The algorithm of the proposed protocol was based on
  the Diffie-Hellman Exchange, but had significant modifications and
  extensions so that the mutual authentication between the mobile user
  and the network was delegated to the serving instead of the home
  network. The protocol design incorporated puzzle schemes that
  demanded unbalanced computing resources on the two sides to mitigate
  Denial-of-Service attacks. \\
  Average Grade & 4.17 / 5
\end{tabular}

\item {\it Beijing Institute of Technology, China}

\begin{tabular}{l p{0.7\textwidth}}
  2001 -- 2005 & B.Sc. Computer Science \& Technology \\
  Average Grade & 85.5 / 100 \\
  Honor & Distinguished Graduates of 2005
\end{tabular}
\end{itemize}

\section{Personal Project}
{\it Trades data collector and analyzer, June 2008 -- present}

Developed a Linux daemon program (programmed in C \& Matlab) to
collect and analyze realtime transaction records on the Stockholm
stock exchange. The program maintained and evolved stochastic
volatility models and made volatility forecast in realtime. Collected
data were managed with a MySQL database.

\section{Non-English Language Skills}
\begin{itemize}
\item Swedish: Informal communications
\item Chinese: Native speaker
\end{itemize}

% \section{Non-English Language Skills}
% \begin{tabular}{l p{0.7\textwidth}}
%   Swedish & No problem with informal communications of talking,
%   reading and writing. ``Swedish B'' passed.\\
%   Chinese (Mandarin) & Native speaker \\
% \end{tabular}

\colorbox{shade}{\textcolor{text1}{
\begin{tabular}{c|p{7cm}}
\raisebox{-1pt}{\Bowtie} & Swedish citizen \\
\raisebox{-2pt}{\textifsymbol{18}} & Kiviksgatan 7C, 21440 Malm\"o, Sweden \\ % Address
\raisebox{-2pt}{\Mobilefone} & +46 70 489 0472 \\ % Phone number
\raisebox{-1pt}{\Letter} & \href{mailto:xie.xiaolei@gmail.com}{xie.xiaolei@gmail.com} \\ % Email address
\Keyboard & \href{http://www.facebook.com/xie.xiaolei}{http://www.facebook.com/xie.xiaolei} \\ % Website
\end{tabular}
}}\\[10pt]

@@

{\raggedleft\textsc{Sep 2008 -- Jan 2011}\par}

{\raggedright\large Development Engineer at \textsc{ST-Ericsson}, Lund\\
  \textit{Software Development}\\[5pt]}

\normalsize{Developed audio low-level software, typically device
  drivers, in the Linux OS.}\\

@@

{\raggedleft\textsc{May 2007 -- Sep 2007}\par}

{\raggedright\large Software Designer at \textsc{Goodmillsystems}, Helsinki\\
  \textit{Software Development}\\[5pt]}

\normalsize{Developed a daemon program that ran on the company's
  smart router product for network traffic monitoring.}\\

@@

{\raggedleft\textsc{Sep 2006 -- April 2007}\par}

{\raggedright\large Software Developer at \textsc{Cardinal Information
    Systems}, Helsinki\\
  \textit{Software development}\\[5pt]}

\normalsize{Implemented the FLUTE protocol for the company's DVB-H mobile-end
  middleware.}\\

%------------------------------------------------
% WORK EXPERIENCE 4
%------------------------------------------------
{\raggedleft\textsc{Feb 2006 - Sep 2006}\par}

{\raggedright\large Game Engineer at \textsc{Digital Chocolate}, Helsinki\\
  \textit{Java  mobile game development}\\[5pt]}

\normalsize{Ported and customized mobile phone games for various
  handsets. Also developed some general tools for game customization.}\\

%------------------------------------------------
% WORK EXPERIENCE 5
%------------------------------------------------
{\raggedleft\textsc{April 2004 - June 2005}\par}

{\raggedright\large Software Engineer at \textsc{Holystone Ltd}, Beijing\\
  \textit{Java Software development}\\[5pt]}

\normalsize{Developed JSP pages and database routines for the
  company's information system.}\\

\section{Programming Skills}
\begin{itemize}
\item Very experienced in C, Matlab
\item Experienced in C++, Python, Java, SQL
\item Very familiar with Linux
\end{itemize}
